\Huge{Complex State Management with Immutability}

### 2022-02-18 Paper.tex
A move toward structure of problem techneques applyingThem

>>>>

% write some problems

\section{Complex State}
% https://medium.com/super-declarative/understanding-state-management-and-why-you-never-will-dd84b624d0e
The term state management has gain traction over the last decade or so with the emergence of wide spread IT solutions along with it the ease of which you can make one of your own from whatever background you come from. And so depending on the underlying scenario the term could stand for:
Data persistence management,
Information flow,
Programming paradigms,
I/O (especially networking and caching), %% TODO: latency table
Application architecture,
Presentation behavior and 
UI templating. So the term state management has been a catch-all term that really means “software engineering” from data modeling to parallel computing.

\subsection{Data Persistence}

%%-----------https://www.researchgate.net/publication/221596019_Analyzing_persistent_state_interactions_to_improve_state_management ---------
A primary challenge to building reliable and secure computer systems is managing the persistent state of the system: all the executable files, configuration settings and other data that govern how a system functions. The difficulty comes from the sheer volume of this persistent state, the frequency of changes to it, and the variety of workloads and requirements that require customization of persistent state. The cost of not managing a system's persistent state effectively is high: configuration errors are the leading cause of downtime at Internet services, troubleshooting configuration problems is a leading component of total cost of ownership in corporate environments, and malware—effectively, unwanted persistent state—is a serious privacy and security concern on personal computers.
%In this paper, we analyze how computer systems dynamically interact with files and configuration settings in an attempt to gain insights into the problem of persistent state management. We analyze over 3648 machine days of these persistent state interactions, collected over an 8 month period from 193 machines. These machines are under real workloads and include Internet servers, corporate desktops, and home machines. We characterize the scope and magnitude of the persistent state management problem today, measuring not only the gross characteristics of persistent state, but also analyzing how it is used by applications, and when administrators and users modify it. We find that monitoring persistent state interactions provides important visibility and show how it can be used as a foundation for building better persistent state management tools.
%%----------------------------------------------------

\subsection{Information Flow}
%%https://thedaylightstudio.com/blog/2018/03/14/what-is-state-in-web-application-development
Application State (a.k.a. Program State) represents the totality of everything necessary to keep your application running.  When we refer to application state we are normally referring to the state of the program as it exists in the contents of its memory.  But what does that mean practically?  How am I to understand that?  It helps to think in extremes.  What happens to information and functionality core to your application if a server goes down and restarts?  You lose whatever was residing in memory.

%This is one of the reasons why in web development we often use stateless resource controllers which disseminate the information necessary to the running of your application in a way that does not rely heavily on holding data for retrieval on the server’s memory.
%% -------------------------------

%% https://dojotoolkit.org/documentation/tutorials/1.6/data_modeling/
 The Model-Viewer-Controller (MVC) is a dominant paradigm for application development. The MVC approach separates key common concerns for organized, manageable application code. Dojo is heavily based on MVC principles, and provides powerful helpers for MVC-structured applications. The foundation of a well-designed MVC application is a solid data model. Here we will see how we can leverage Dojo object stores and Stateful objects to create a robust model that can be used in the view and controller code.
 The model is the M in MVC. The data model represents the core information that your application is being used to access and manipulate. The model is the center of your application
%%--------------------------------------

%%%%https://www.researchgate.net/publication/2716493_The_Role_of_Distributed_State
Distributed state offers the potential for improving the performance, coherency, and reliability of distributed systems. Unfortunately, distributed state also introduces consistency problems, crash sensitivity, time and space overheads, and complexity; these problems make it difficult to achieve the potential benefits. This paper describes the advantages and disadvantages of distributed state, and presents the NFS and Sprite file systems as examples of different tradeoffs. It does not appear possible to achieve all the advantages of distributed state and also avoid all the problems; rather, system designers must make compromises based on the needs of their individual environments. The Role of Distributed State February 19, 1990 1. Introduction Webster's New World Dictionary defines state as "a set of circumstances or attributes characterizing a person or thing at a given time" [4]. State plays a fundamental role in all computer systems. One way of characterizing computation is as a ...
%----------------

Current solutions pitfalls
% http://www.padsweb.rwth-aachen.de/wvdaalst/publications/p514.pdf
\subsubsection{Missing data}
s the situation where some data element needs to be accessed, i.e. read or destroyed, but either it has never been created or it has been deleted without having been created again.
\subsubsection{Inconsistent Data} 
Data is inconsistent if a task is using this data while some other task (or another instance of the same task) is writing to this data or is destroying it in parallel.
%-----------------------------

\subsection{Programming Paradigms}
% https://www.geeksforgeeks.org/introduction-of-programming-paradigms/
Programming paradigm is an approach to solve problem using some programming language or also we can say it is a method to solve a problem using tools and techniques that are available to us following some approach.
%----------------------------------------
And so most paradigms have their own opinion on data manipulation for example: Procedural \& Object Oriented paradigms allows more access to data modifying (destructive updates), deleting. Others like Logic \& Functional doesn't allow them.

\subsection{I/O (especially networking and caching)}

%-------------------------------------------------------

%this format problems tech solutions
\subsection{Using Immutability}
